---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

# clustlearn

The goal of clustlearn is to provide a set of functions to perform clustering analysis along with comprehensive explanations of the algorithms, their pros and cons, and their applications.

## Installation

You can install the released version of clustlearn from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("clustlearn")
```

You can install the development version of clustlearn from [GitHub](https://github.com/) with:

``` r
devtools::install_github("Ediu3095/clustlearn")
```

## Example

This is a basic example which shows you how to cluster a dataset:

```{r example_cluster}
# # Load the clustlearn package
# library(clustlearn)

# Perform the clustering (the clustlearn:: prefix is not necessary)
cl <- clustlearn::dbscan(clustlearn::db1, 0.3)

# Plot the results
out <- cl$cluster == 0
plot(clustlearn::db1[!out, ], col = cl$cluster[!out], pch = 20, asp = 1)
points(clustlearn::db1[out, ], col = max(cl$cluster) + 1, pch = 4, lwd = 2)
```

This is yet another basic example which shows you how to see the step-by-step procedure of the clustering algorithm:

```{r example_procedure}
# # Load the clustlearn package
# library(clustlearn)

# Perform the clustering (the clustlearn:: prefix is not necessary)
# The details argument is set to TRUE to see the step-by-step procedure
cl <- clustlearn::agglomerative_clustering(
  clustlearn::db5[1:6, ],
  'single',
  details = TRUE,
  waiting = FALSE
)
```

<!-- You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this. You could also use GitHub Actions to re-render `README.Rmd` every time you push. An example workflow can be found here: <https://github.com/r-lib/actions/tree/v1/examples>. -->
